\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{casual}

\usepackage[utf8]{inputenc}

% personal data
\firstname{Jonathan}
\familyname{Sharyari}
\title{Software Engineer}
%\newline \small{\texttt{\textbf{Homepage: {\color{web}\weblink{http://lukas.fyi}}}}}}
%\title{BCS student of Uppsala \newline \small{\texttt{\textbf{Homepage: {\color{web}\weblink{http://www.mindlevel.net}}}}}}
%\address{Office 719 SEO\\ 851 S. Morgan St.}{Chicago, IL}
%\extrainfo{\newline \color{red}Don't miss the other page$\rightarrow$}
\phone{+46704-16 85 00}
\email{sharyari@gmail.com}
\address{Flogsavägen 59E}{75273 Uppsala}
\homepage{https://github.com/sharyari}
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}
\nopagenumbers{}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%------------------------------------\photo[64pt][0.4pt]{picture} ----------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{\textbf{Experience}}
\subsection{\textbf{Work Experience}}
\cventry{2018 -- Current}{\textbf{Software Engineer}}{}{}{Sigicom AB}{
    Software development and DevOps with a focus on Erlang and Python \textsc{api} backend development.
\section{Key Responsibilities}
\begin{itemize}
    \item Setup and management of Xen virtualized servers in production
    \item Automation ans deployment with ansible
    \item Continuous integration and deployment using Concourse CI
    \item \textsc{cvs} management
    \item Python \textsc{api} development using Django web framework
    \item Erlang \textsc{rest api} development with Decirest
    \item Coordinating and executing releases to production  
\end{itemize}
\section{Key Achievements}
\begin{itemize}
    \item Live migration and upgrade of physical and virtual nodes of a production system 
    \item Transition from Python 2 to 3 of a major code base
\end{itemize}
}

\cventry{2015 -- 2018}{\textbf{Personal Assistent}}{}{}{Alma Assistans}{
    Assisting an elderly person with their daily activities.
}

\cventry{2009 -- 2011}{\textbf{Various}}{}{}{Uplands Nation}{
    Various responsibilities, ranging from bartending to staff management and event planning and contract negotiations.
}
\cventry{Jun-Aug 2009/2010}{\textbf{Quality Assurance}}{}{}{St Jude Medical}{
    Receiving, managing and documenting faulty medical products.
}
\section{\textbf{Education}}
\cventry{2008--2015}{\textbf{Master of Science and Technology}}{Computer Science}{\newline University of Uppsala}{Sweden}{}{}
\cventry{2012--2013}{\textbf{Master of Science and Technology}}{Computer Science}{\newline Freie Universität Berlin}{Germany}{}{}

\subsection{\textbf{Thesis}}
\cventry{}{\textbf{Master Thesis}}{Uppsala University}{Uppsala}{}{
Algorithmic Analysis of Channel Machines Using Small Model}

\subsection{\textbf{Some Open Source projects}}
\cventry{}{\textbf{Pyrlang and Term}}{}{}{}{
    Erlang node implementation and \textsc{etf} parser in python.
}
\cventry{}{\textbf{Decirest}}{}{}{}{
    REST API framework for erlang.
}
\cventry{}{\textbf{Swe-crypto-tax}}{}{}{}{
    Tool for generating tax form entries for crypto transaction.
}

\renewcommand{\cvcomputer}[2]{\cvline{#1}{\small#2}}
\section{\textbf{Computer skills}}
\cvcomputer{OS}{Linux, Windows}
\cvcomputer{Programming}{Erlang, Python, C, Rust, Android, Haskell, Bash}
\cvcomputer{Databases}{PostgreSQL, InfluxDB, Riak}
\cvcomputer{Rev. control}{Git, Mercurial}
\cvcomputer{Editors/IDE}{Vim, IntelliJ, Eclipse, MS Code}
\cvcomputer{Typography}{\LaTeX, Office}
\cvcomputer{Netwroking}{DNS, HAProxy, Nginx}
\cvcomputer{Virtualization}{Xen, Ganeti, VirtualBox, Vagrant}
\cvcomputer{Other}{
                   Containers\newline
                   System Administration\newline 
                   Microcontroller Programming\newline 
                   Hardware replacement}

\section{\textbf{Other}}
\cventry{}{\textbf{Languages}}{}{}{}{
    English (Fluent)\newline
    Swedish (Mother tounge)\newline
    German (Lived in Germany, C-Level studies at the University)\newline
    Persian (Mother tongue)\newline
    Spanish Basics (Backpacked Latin America)}
%\cventry{}{\textbf{8 references}}{}{}{}{}

\end{document}
